Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-12-09 vesicle_code/docs/permeableVes/main.tex
yny

\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}.  For example, erythrocytes demonstrate efficient exchange of water to participate in efficient body water homeostasis \cite{SugieIntaglietta2018_AmJPhysiolHCP}.  Another example is the simultaneous regulation of cell volume and the cell membrane tension during cell migration through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS}.

>>>>

\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}.  For example, erythrocytes participate in efficient body water homeostasis by regulating its exchange of water  \cite{SugieIntaglietta2018_AmJPhysiolHCP}.  Another example is the simultaneous regulation of cell volume and the cell membrane tension during cell migration through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS}.
